Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-28 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:28	22:42:14	(Fri28.Aug)

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={A Fast GPU Sonar Simulator for Automatic Target Recognition},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
% \ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
% \else
%    \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
%    \usepackage{breakurl}                        % Allows 'dvips' driver to break links
% \fi

@@

\newcommand\multimedia[1]{\textbf{{\color{red}[#1]}}}

@@

Adaptive beamformers are generally not so simple. They allow the weights/delays to change to adjust the array response to better fit the incoming wavefield. Of these methods the minimum variance distortionless response (MVDR) beamformer is perhaps the best studied and well known.

@@

Media file \multimedia{Media Movie 1} shows how \Fig{mvdr_selected_windows} changes as a function of the MVDR subarray length $L$. It demonstrates that at $L$=1 the window responses are rectangular in all areas in the image. At $L$=2 we can observe that pixels in highlight are processed with windows with slightly varying amplitude responses, but with zero locations on similar locations and highlight regions being

>>>>

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    bookmarksnumbered ]{hyperref}
\else
   \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}
   \usepackage{breakurl}                        % Allows 'dvips' driver to break links
\fi

@@

% \newcommand\multimedia[1]{\textbf{{\color{red}[#1]}}}
\newcommand\multimedia[2]{\href{#1}{#2}}

\newcommand\mediaPath{gfx/media}
\newcommand\mediaI{\multimedia{\mediaPath/media1.mp4}{Media Movie 1}}
\newcommand\mediaII{\multimedia{\mediaPath/media2.mp4}{Media Movie 2}}

@@

Adaptive beamformers allow the weights and delays to change to adjust the array response to better fit the incoming wavefield. One of the most extensively studied methods here is the minimum variance distortionless response (MVDR) beamformer.

@@

\mediaI{} shows how \Fig{mvdr_selected_windows} changes as a function of the MVDR subarray length $L$. It demonstrates that at $L$=1 the window responses are rectangular in all areas in the image. At $L$=2 we can observe that pixels in highlight are processed with windows with slightly varying amplitude responses, but with zero locations on similar locations and highlight regions being
